---
title: "R Notebook"
output: html_notebook
---

My goal here is to write code to convert my Facebook post history into Day One Journal format. I may try to turn this into a Shiny app as well, as a learning experience.

```{r}
library(jsonlite)
library(lubridate)
library(anytime)


```

So each your_posts.json has 5 components:

* timestamp - timestamp
* attachments - associated links or photos
* data - the post itself
* title - "Eric Posted in Washington Place" or "Eric updated his status"
* tags - People that you tagged


Facebook outputs text incorrectly coded as UTF-8 as described [here](https://stackoverflow.com/questions/50008296/facebook-json-badly-encoded). For example apostrophes coded as "Ericâ\u0080\u0099s" I used iconv below to fix it.

```{r}

FBposts <- fromJSON("/Users/eric/Documents/Eric_Personal_Projects/facebook-ericcrandall0_json/posts/your_posts_1.json")

title <- FBposts$title
timestamp <- anytime(FBposts$timestamp)
tags <- FBposts$tags
attachments <- FBposts$attachments
data <- FBposts$data

for(p in length(data)){
  
}

FBconvert <- function(index, title, timestamp, tags, attachments, data){
  
  text<- message(paste(title[index],iconv(data[[index]]$post[1], "UTF-8", to = "latin2"), sep = "\n"))
  entry <- c(timestamp[index], print(title[index],"\n")
  
}
  




```